---
title: '2016'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Read File

```{r}
library(igraph)
nodes <- read.csv("/Users/yunting/Desktop/year2016/nodes.csv", header=T, as.is=T)
links <- read.csv("/Users/yunting/Desktop/year2016/edges.csv", header=T, as.is=T)

head(nodes)
head(links)

nrow(nodes); length(unique(nodes$id))
nrow(links); nrow(unique(links[,c("from_name", "to_name")]))

links <- aggregate(links[,3], links[,-3], sum)
links <- links[order(links$from_name, links$to_name),]
colnames(links)[3] <- "weight"
rownames(links) <- NULL
```

## weighted
```{r pressure, echo=FALSE}
net <- graph_from_data_frame(d=links, vertices=nodes, directed=T)

colrs <- c("deepskyblue","orangered", "lightseagreen")
V(net)$color=V(net)$aff
V(net)$color=gsub("DEM","deepskyblue",V(net)$color) 
V(net)$color=gsub("REP","orangered",V(net)$color) 
V(net)$color=gsub("UNK","lightseagreen",V(net)$color)
E(net)$arrow.size <- .5
E(net)$width <- E(net)$weight/50

plot.igraph(net, vertex.label=nodes$id, vertex.label.cex = .2, edge.color="orange")
legend(x= -1, y= -1, c("DEM","REP", "UNK"), pch=21,
       col="#777777", pt.bg=colrs, pt.cex=2, cex=.8, bty="n", ncol=1)
```

## betweeness
```{r pressure, echo=FALSE}
plot.igraph(net, vertex.label=nodes$id, vertex.label.cex = .25, edge.color="orange", vertex.size=betweenness(net)*4 )
legend(x= -1, y= -1, c("DEM","REP", "UNK"), pch=21,
       col="#777777", pt.bg=colrs, pt.cex=2, cex=.8, bty="n", ncol=1)
```

## degree
```{r pressure, echo=FALSE}
plot.igraph(net, vertex.label=nodes$id, vertex.label.cex = .2, edge.color="orange", vertex.size=degree(net)*1 )
legend(x= -1, y= -1, c("DEM","REP", "UNK"), pch=21,
       col="#777777", pt.bg=colrs, pt.cex=2, cex=.8, bty="n", ncol=1)
```

## Simplify
```{r, echo=TRUE}
hist(links$weight)
mean(links$weight)
sd(links$weight)
# keep the weight that weights higher than the mean of the network
cut.off <- mean(links$weight)
net.sp <- delete_edges(net, E(net)[weight < cut.off])
E(net)$width <- E(net)$weight/30
plot(net.sp, vertex.label=nodes$id, vertex.label.cex = .2, layout=layout.circle)
legend(x= -1, y= -1, c("DEM","REP", "UNK"), pch=21,
       col="#777777", pt.bg=colrs, pt.cex=2, cex=.8, bty="n", ncol=1)
```

## heatgraph
```{r, echo=TRUE}
netm <- get.adjacency(net, attr="weight", sparse=F)
colnames(netm) <- V(net)$name
rownames(netm) <- V(net)$name
palf <- colorRampPalette(c("gold", "dark orange"))
heatmap(netm[,17:1], Rowv = NA, Colv = NA, col = palf(100),scale="none", margins=c(10,10) )
```

## transitivity
```{r, echo=TRUE}
transitivity(net, type="global") # net is treated as an undirected network 
transitivity(as.undirected(net, mode="collapse")) # same as above 
transitivity(net, type="local")
triad_census(net) # for directed networks
```

## Diameter
```{r, echo=TRUE}
diameter(net, directed = F, weights=NA)
diameter(net, directed = F)
diam <- get_diameter(net, directed=T)
diam

vcol <- rep("gray40", vcount(net))
vcol[diam] <- "gold"
ecol <- rep("gray80", ecount(net))
ecol[E(net, path=diam)] <- "orange"
# E(net, path=diam) finds edges along a path, here  diam  
plot(net, vertex.color=vcol, edge.color=ecol, edge.arrow.mode=0, vertex.label=nodes$id, vertex.label.cex = .2)
```

## Histogram of node degree
```{r, echo=TRUE}
deg <- degree(net, mode = "all")
hist(deg, breaks=1:vcount(net)-1, main="Histogram of node degree")
```

## degree distribution
```{r, echo=TRUE}
deg.dist <- degree_distribution(net, cumulative=T, mode="all") 
plot( x=0:max(deg), y=1-deg.dist, pch=19, cex=1.2, col="orange", xlab="Degree", ylab="Cumulative Frequency")
```

## Hubs and authorities
```{r, echo=TRUE}
hs <- hub_score(net, weights=NA)$vector
as <- authority_score(net, weights=NA)$vector
par(mfrow=c(1,2))
plot(net, vertex.size=hs*15, main="Hubs", vertex.label=nodes$id, vertex.label.cex = .15)
plot(net, vertex.size=as*20, main="Authorities", vertex.label=nodes$id, vertex.label.cex = .15)
```

## Distances and paths
```{r, echo=TRUE}
mean_distance(net, directed=F)
distances(net) # with edge weights 
distances(net, weights=NA) # ignore
```

## Subgroups and Communities
```{r, echo=TRUE}
net.sym <- as.undirected(net, mode= "collapse", edge.attr.comb=list(weight="sum", "ignore"))
cliques(net.sym) # list of cliques 
sapply(cliques(net.sym), length) # clique sizes 
largest_cliques(net.sym) # cliques with max number of nodes

vcol <- rep("grey80", vcount(net.sym)) 
vcol[unlist(largest_cliques(net.sym))] <- "gold" 
plot(as.undirected(net.sym), vertex.label=V(net.sym)$name, vertex.color=vcol, vertex.label=nodes$id, vertex.label.cex = .3)
```

## Community detection
```{r, echo=TRUE}
ceb <- cluster_edge_betweenness(net) 
plot_dendrogram(ceb, cex = 0.3)
#plot(ceb, net, vertex.label=nodes$id, vertex.label.cex = .2)
length(ceb)
membership(ceb)
modularity(ceb)
crossing(ceb, net)
```

## Community detection based on propagating labels
```{r, echo=TRUE}
clp <- cluster_label_prop(net)
plot(clp, net, vertex.label=nodes$id, vertex.label.cex = .2)
```

## Community detection based on greedy optimization of modularity
```{r, echo=TRUE}
cfg <- cluster_fast_greedy(as.undirected(net))
plot(cfg, net, vertex.label=nodes$id, vertex.label.cex = .2, as.undirected(net))
```

## K-score decomposition
```{r, echo=TRUE}
kc <- coreness(net, mode = "all")
plot(net, vertex.size=kc*6, vertex.label=kc, vertex.color=colrs[kc])
```

## assortativity and Homophily
```{r, echo=TRUE}
assortativity_degree(net, directed = F)
```